IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-08 paper/concrete.tex
Remove some duplication
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

If the operational rules are adapted na\"ively to this new setting,
then non-interference can be violated.  In particular, it is not
sound to share references to a heap cell between different tasks.
Otherwise, information can be trivially leaked by copying
secret data to a shared reference in one task, and then
reading it again by a another task with a lower label.
What we would like is a way of characterizing safe modifications to
the semantics which preserve non-interference.
The intention of our single heap implementation is to permit
efficient execution while \emph{conceptually maintaining isolation between
tasks} (by not allowing sharing of references between them).
This intuition of having a different (potentially more efficient)
concrete semantics that behave like the abstract semantics
can be formalized by the following definition:

@@

As a concrete instantiation of this proof technique, we show
how to make our single heap IFC language precise and
ensure its non-interference using the techniques presented.
First, we can construct the restricted language
|restrictedLangNoRef alpha targetLangML|, where |noRefs| is
the family of always valid predicates, except for the ones for
\textsc{I-sandbox} and \textsc{I-send}, which we define as
\[ P(|ie|) = (\mathcal{AV}(|ie|) = \emptyset{}) \]
where $\mathcal{AV}(|ie|)$ denotes the set of address variables in |ie|.
That is, we do not restrict any rules except for \textsc{I-sandbox}
and \textsc{I-send}.
Since $P$ only depends on |ie|, which is part of the current
task and thus never erased w.r.t.\ the label of the first task,
this language satisfies non-interference by Theorem~\ref{thm:restricted}.

>>>>

If the operational rules are adapted na\"ively to this new setting,
then non-interference can be violated: as we mentioned earlier,
shared mutable cells could result in violation of noninterference.
What we would like is a way of characterizing safe modifications to
the semantics which preserve non-interference.
The intention of our single heap implementation is to permit
efficient execution while \emph{conceptually maintaining isolation between
tasks} (by not allowing sharing of references between them).
This intuition of having a different (potentially more efficient)
concrete semantics that behave like the abstract semantics
can be formalized by the following definition:

@@

As a concrete instantiation of this proof technique, we show
how to make implement our IFC language using a single heap and
ensure its non-interference using the techniques presented.
First, we can construct the restricted language
|restrictedLangNoRef alpha targetLangML|, where |noRefs| is
the family of always valid predicates, except for the ones for
\textsc{I-sandbox} and \textsc{I-send}, which we define as
\[ P(|ie|) = (\mathcal{AV}(|ie|) = \emptyset{}) \]
where $\mathcal{AV}(|ie|)$ denotes the set of address variables in |ie|.
That is, we do not restrict any rules except for \textsc{I-sandbox}
and \textsc{I-send}.
Since $P$ only depends on |ie|, which is part of the current
task and thus never erased w.r.t.\ the label of the first task,
this language satisfies non-interference by Theorem~\ref{thm:restricted}.
